\ProjectName{}: Data Imputation as a Query Optimization

### 2016-12-14 paper/experiments.tex
paper: minor word changes
paper: reworded explanation of experiments table

The queries on the ACS data all consist only of selections, filters, and aggregations.
The ACS data is contained in a single table, so there are relatively few join queries that are interesting on this data set and remain relevant for analysts, rather
than contrived solely for the purpose of experimentation.
However, even with select, filter, and aggregate, there are interesting choices to make with imputation placement. In order to explore joins, we leverage the synthetic
dataset and write various ad-hoc queries.

@@

\begin{table}
  \centerfloat
  \input{runtimes}
    \caption{Error ($\epsilon$, planning time ($t_p$), and running time ($t_r$)i or queries
    with different imputation levels. Base error is the root-mean-square error (RMSE) between the query run on clean
    data and the query run on dirty data without imputation.}
  \label{fig:experiments}
\end{table}

Table~\ref{fig:experiments} provides a summary of our experimental results.
We run each query in four configurations: without imputation on clean data, without imputation on dirty data, and with imputation on dirty data for $\alpha = 0$ and $\alpha = 1$.
When a query returns a relation of the same ``shape'' (same number of tuples and same schema) on both clean and dirty data, we can compute an error value.
For our experiments, we report root-mean-square error (RMSE).
For imputations, we run queries using the two extreme values of $\alpha$: 0 and 1, representing a focus on runtime and on information loss, respectively.
For each query, the table displays the error between the query run on clean data and the query run on dirty data with imputation and the running time in seconds.

>>>>

The queries on the ACS data all consist only of projections, selections, and aggregations.
The ACS data is contained in a single table, so there are relatively few join queries that are interesting on this data set and remain relevant for analysts, rather
than contrived solely for the purpose of experimentation.
However, even with select, filter, and aggregate, there are interesting choices to make with imputation placement. In order to explore joins, we leverage the synthetic
dataset and write various ad-hoc queries.

@@

\begin{table}
  \centerfloat
  \input{runtimes}
    \caption{Base error, change in error and and running time for queries
    with different imputation levels. Base error is the root-mean-square error (RMSE) between the query run on clean
    data and the query run on dirty data without imputation. Change in error is relative to the base error.}
  \label{fig:experiments}
\end{table}

Table~\ref{fig:experiments} provides a summary of our experimental results.
We run each query in four configurations: without imputation on clean data, without imputation on dirty data, and with imputation on dirty data for $\alpha = 0$ and $\alpha = 1$.
When a query returns a relation of the same ``shape'' (same number of tuples and same schema) on both clean and dirty data, we can compute an error value.
For our experiments, we report root-mean-square error (RMSE) for the base error (i.e. the error in the dirty data without imputation with respect to the clean data) and the change
in RMSE for the imputed plans.
For imputations, we run queries using the two extreme values of $\alpha$: 0 and 1, representing a focus on runtime and on information loss, respectively.
For each query, the table displays the base error, the change in error in both imputation scenarios, and the running time in seconds.
